---
title: "ejercicio"
author: "seyhun"
date: "6/28/2019"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

# Title:RMarkdown Exercise

## Abstract  

I am creating an rmarkdown document

## Introduction 

bla bla bla

## Material and Methods

### Participants

A lot of parcitipants participated 

### Materials

We used very cool tools

## Results


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(haven)
Cancer_screening_risk_literacy_R1 <- read_sav("C:/Users/fustun/Desktop/githubproject/Cancer screening risk literacy R1.sav")
data=Cancer_screening_risk_literacy_R1 

corr_test = cor.test(data$screenbeliefs,data$numeracy, method = "spearman")

library (tidyverse)


#remotes::install_github("easystats/correlation")
# remotes::install_github("easystats/report")
require("correlation")
require("report")
table <- data %>% 
   select(numeracy,sciliteracy, knowlR1, compR1, benefits, harms, recommendation ) %>% 
    correlation() %>% 
    report() %>% 
    to_table()
  
  knitr::kable(table)

```


We are awesome scientists

### Exp I

Controls thought the experiment was fun
  
### Exp II 

Patients also thought the experiment was fun
  
## Discussion

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results='asis'}
library(stringi)
stri_rand_lipsum(nparagraphs = 1)
```


# Bibliography

  